Current and future constraints on primordial magnetic fields

### 2017-02-01 pmf.tex
ifi2 edits

\begin{figure*}[htb]\centering
\includegraphics[width=0.9\textwidth,clip,trim={1.5cm 12.cm 5.5cm 4cm}]{pmf_templates.pdf}
  \caption[CMB polarization from PMFs]{
  The expected contributions to CMB B-modes. \textbf{\textcolor{magenta}{CF: log y should show the degeneracy better}}
  The red line shows the expected lensing B-mode power in the \planck{} best-fit \lcdm{} cosmology. 
  The dark green line corresponds to the contribution from inflationary gravitational waves for $r=0.05$; the solid black line is the sum of the inflationary gravitational wave and lensing B-modes. 
  The dashed purple line shows the nearly-scale invariant ($n_B=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
  As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate in a power spectrum (2-point) analysis.
  %However, if excess power on these scales is detected, higher order moments of the map (i.e.~4-point estimators) might be used to discriminate between   the inflationary and PMF explanations. 
      \label{fig:pmf-bb}
  }
\end{figure*}

>>>>

\begin{figure*}[htb]\centering
\includegraphics[width=0.9\textwidth,clip,trim={1.cm 12.cm 6cm 5cm}]{pmf_templates.pdf}
  \caption[CMB polarization from PMFs]{
  The expected contributions to CMB B-modes.
  The red line shows the expected lensing B-mode power in the \planck{} best-fit \lcdm{} cosmology. 
  The dark green line corresponds to the contribution from inflationary gravitational waves for $r=0.05$; the solid black line is the sum of the inflationary gravitational wave and lensing B-modes. 
  The dashed purple line shows the nearly-scale invariant ($n_B=-2.9$) PMF template used in this work, scaled to \apmf{} = 0.2 (i.e.~\bpmf{}=1.7\,nG) to match the gravitational wave signal. 
  As can be seen, the tensor contribution from PMFs at large angular scales (low $\ell$) closely resembles the expected inflationary gravitational wave signal, and the two signals are effectively degenerate in a power spectrum (2-point) analysis.
  %However, if excess power on these scales is detected, higher order moments of the map (i.e.~4-point estimators) might be used to discriminate between   the inflationary and PMF explanations. 
      \label{fig:pmf-bb}
  }
\end{figure*}
